Fast, Scalable Phrase-Based SMT Decoding

### 2016-05-06 acl.2016/acl2016.tex
changes

We shall seek to improve decoding speed by replacing the operating system's general purpose memory management with our own custom memory management scheme. In time-critical parts of the decoder, memory will be allocated from a memory pool.

@@

To further increase memory management speed, objects are not deleted, instead the memory pool is simply reset and reused for each input sentence. This can result in high memory usage so object queues are available for high-churn objects which allows the decoder to re-use portion of the memory pool before it is reset. The object queues are LIFO so that recently accessed memory are used, increasing CPU cache hits.

>>>>

We shall seek to improve decoding speed by replacing the operating system's general purpose memory management with our own custom memory management scheme. Memory will be allocated from a memory pool rather than use the operating system's general purpose allocation functions.

@@

To further increase memory management speed, objects are not deleted, instead the memory pool is simply reset and reused for each input sentence. Not deleting objects can result in unacceptably high memory usage so object queues are available for high-churn objects which allows the decoder to re-use portion of the memory pool before it is reset. The object queues are LIFO so that recently accessed memory are used, increasing CPU cache hits.
